Empirical Study of Scientific Computer Software: Objectives and Research Questions

### 2020-06-11 OverallResearchProposal/ObjectivesAndResearchQuestions.tex
Addition of some ideas for the next set of edits to the research questions

\textbf{What is needed to produce sustainable \{software + artifacts\}?}\\

@@

We define sustainable softifacts, as follows: \emph{Sustainable softifacts
  satisfy, for a reasonable amount of energy, the software requirements for the
  present, while also being maintainable, reusable and reproducible for the
  future.}  This definition is a specialization of the general definition of
sustainable development from \citet{Brundtland1987}, as discussed in
Section~\ref{Sec_Context}.  The notion of ``reasonable effort'' is part of the
definition of sustainability, but reasonable cannot be completely defined
because what is reasonable is going to depend on the context.  Problems that are
large, complex and/or critical are going to have a greater ``budget'' of time
and energy.  When comparing different alternatives for processes and
methodologies, preference would be given to the alternative that costs less
effort, assuming that this alternative achieves the same (or a higher) level of
sustainability as its competition.  The assumptions listed in the next section
(Section~\ref{Sec_Context}) outline the typical space of problems where it makes
sense to aim for sustainable softifacts.

@@

@@

@@

\begin{itemize}
\item The software project is going to be long lived, where long life means at
  least 10 years.
\item The softifacts should interest multiple stakeholders (not just the
  original developer), with different interests and backgrounds.
\item The software is safety relevant, such as software for nuclear safety,
  medical imaging or computational medicine.
\item The software explicitly, or implicitly, is part of a program family of
  related software.  When the program family assumption means that there are
  related programs that are less effort to design and build together than to
  design and build as separate projects.  Program family development depends on
  satisfying three hypotheses \citep{Weiss1997}:
\begin{itemize}
\item Redevelopment hypothesis – most software development involved in producing
  an individual family members should be redevelopment because the family
  members have so much in common.
\item Oracle Hypothesis – the changes that are likely to occur during the soft-
  ware’s \ad{software's} lifetime are predictable.
\item Organizational Hypothesis – designers can organize the software and the
  development effort so that predicted changes can be made independently.
\end{itemize}
\item The project recognizes that software artifacts other than the code are
  relevant.
\item The domain of the software project is well understood.  This assumption is
  related to the oracle hypothesis.
\end{itemize}

Although this study is not specifically restricted to open-source software, for
practical reasons (especially the lack of access to the code), commercial
software will not be strongly emphasized.

>>>>

\textbf{What is needed to produce \{software + artifacts\} sustainably?}\\

@@

We define sustainable softifacts, as follows: \emph{Sustainable softifacts
  satisfy, for a reasonable amount of effort, the software requirements for the
  present, while also being maintainable, reusable and reproducible for the
  future.}  This definition is a specialization of the general definition of
sustainable development from \citet{Brundtland1987}, as discussed in
Section~\ref{Sec_Context}.  The notion of ``reasonable effort'' is part of the
definition of sustainability, but reasonable cannot be completely defined
because what is reasonable is going to depend on the context.  Problems that are
large, complex and/or critical are going to have a greater ``budget'' of time
and energy.  When comparing different alternatives for processes and
methodologies, preference would be given to the alternative that costs less
effort, assuming that this alternative achieves the same (or a higher) level of
sustainability as its competition.  \wss{reasonable effort, without a large
  cost, means productivity} The assumptions listed in the next section
(Section~\ref{Sec_Context}) outline the typical space of problems where it makes
sense to aim for sustainable softifacts.

@@

what else do we need - knowledge - knowledge captured in softifacts.  - overlap
plus duplication - required and desired, but still want to be productive.  To be
productive, want to say once and view as needed.  Suggests generation - maybe
put this elsewhere?

@@

- what is needed to produce softifacts sustainably motivates our ideal process
(sequence of choices).

@@

- number or name assumptions

\begin{enumerate}
\item The software project is going to be long lived, where long life means at
  least 10 years.
\item The softifacts should interest multiple stakeholders (not just the
  original developer), with different interests and backgrounds.
\item The software is safety relevant, such as software for nuclear safety,
  medical imaging or computational medicine.
\item \wss{this one is about feasibility - separate this out} The software explicitly, or implicitly, is part of a program family of
  related software.  When the program family assumption means that there are
  related programs that are less effort to design and build together than to
  design and build as separate projects.  Program family development depends on
  satisfying three hypotheses \citep{Weiss1997}:
\begin{itemize}
\item Redevelopment hypothesis – most software development involved in producing
  an individual family members should be redevelopment because the family
  members have so much in common.
\item Oracle Hypothesis – the changes that are likely to occur during the soft-
  ware’s \ad{software's} lifetime are predictable.
\item Organizational Hypothesis – designers can organize the software and the
  development effort so that predicted changes can be made independently.
\end{itemize}
\item The project recognizes that software artifacts other than the code are
  relevant.
\item The domain of the software project is well understood.  This assumption is
  related to the oracle hypothesis. \wss{related to feasibility}
\end{enumerate}

- program family comes up to make it economically feasible, not necessary, but
important (JC gave example of space probe - not a family, but still makes sense
to do it right.)
- sustainable - part of reasonable effort
Although this study is not specifically restricted to open-source software, for
practical reasons (especially the lack of access to the code), commercial
software will not be strongly emphasized.
